High-Performance Data Analysis on JANUS using Apache Spark

### 2013-12-18 paper.tex
Typos!
revised first part of page rank description

\subsubsection{PageRank}   
Since Spark system is an in-memory cluster computing system, the power of such a system should be exploited by applications that runs several iterations on the same data.

As an example of iterative algorithms the \emph{Page Rank} algorithm was chosen.
The original pagerank algorithm was developed by Google websearch engine which enabled them to rank the webpages in their search engine.

\emph{Data set}:
The source of the dataset is DBPedia, a crowd sourced community that extracts structured information from wikipedia and makes it available on the web. \citep{[??]} There are different formats of wikipedia datasets available online. For our experiments we chose the wikipedia pagelink dataset \citep{[??]} , this contains
internal links between the DBPedia instances extracted from the internal links of the wikipedia articles making it apt for the any datamining related analysis including Pagerank algorithm. Therefore this dataset was chosen for the experiment.
The overall size of this dataset is 25GB.
The format of the data is \{ source url \} \{ some configuration \} \{ dest url \}
For the pagerank algorithm, only the source url and the dest url is needed.Therefore the dataset was was preprocessed to filter out the only the necessary information.

If the entire dataset is assumed to be represented by a huge graph, then here each DBPedia instance maps to a wikipedia article or a page which inturn could be mapped to a vertex of the graph. And the links between the instances could be mapped to  
edges of the graph.

@@

For the pagerank algorithm, as previously explained the vertices are pages and the edges are links.The list of messages generated at every iteration is the contribution of the pagerank for all its outgoing links.

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=90mm]{images/scalability.png}
        \caption{Scalability Test for Pagerank}
        \label{fig:scalability}
    \end{figure}

@@

% pagerank test 1
% pagerank test 2
% ...

>>>>

\subsubsection{PageRank}   
Since Spark is an in-memory cluster computing system, the power of such
a system should be exploited by applications that runs several iterations on
the same data.  One such iterative algorithm we choose to employ was
\emph{PageRank}.  The original PageRank algorithm was developed by Google which
enabled them to rank the webpages in their search engine.

\emph{Data set}:
We obtained the data used for these tests from DBPedia, a crowd sourced
community that extracts structured information from Wikipedia and makes it
available on the web. \citep{[??]} There are different formats of Wikipedia
datasets available online. For our experiments we chose the Wikipedia pagelink
dataset \citep{[??]} , this contains internal links between the DBPedia
instances extracted from the internal links of the Wikipedia articles making it
apt for the any datamining related analysis including PageRank algorithm.
Therefore this dataset was chosen for the experiment.  The overall size of this
dataset is 25GB.  The format of the data is of the form: \\

\centering
\{ source url \} \{ some configuration \} \{ dest url \} \\

For the PageRank algorithm, only the source url and the dest url is
needed. Therefore the dataset was was preprocessed to filter out only the
necessary information.  If the entire dataset is assumed to be represented by a
huge graph, then here each DBPedia instance maps to a Wikipedia article or a
page which inturn could be mapped to a vertex of the graph. The links
between the instances could then be mapped to edges of the graph.

@@

For the PageRank algorithm, as previously explained the vertices are pages and the edges are links.The list of messages generated at every iteration is the contribution of the PageRank for all its outgoing links.

@@

    \begin{figure}[H]
        \centering
        \includegraphics[width=90mm]{images/scalability.png}
        \caption{Scalability Test for PageRank}
        \label{fig:scalability}
    \end{figure}

@@

% PageRank test 1
% PageRank test 2
% ...
